The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 also extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.

 % Reverse shock

@@

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees\

>>>>

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 also extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc
 indicating that the innermost bubbles are an expanding reverse shock.

@@

  \subsection{X-ray}
  \label{X-ray}
  The X-ray emissivity is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight\
  pointing away from the solar position at $(R_{\odot},0,0)=(8,0,0)$ kpc\
  with angular resolutions of 0.5 degrees, where $R_{\odot}$ is the Sun-GC distance.
